The problem and promise of scale in multilayer animal social networks

### 2020-02-12 paper/manuscript.Rmd
reln between social and hab para

The link between habitat and sociality has been

Despite not in a multilayer network context, the link between habitat and
sociality has been previously investigated. Fortin et al. (2009) evaluated
habitat selection and group formation and division in bison. They observed
contrasting group sizes in meadows and forests as well as identified predation
risk avoidance as a main factor in their habitat selection [@Fortin_2009]. A
review of the influence of habitat fragmentation on sociality noted decreased
group size in small patches compared to large, continuous landscapes
[@Banks_2007]. Finally, McLoughlin (2000) showed variable responses in brown
bears (*Ursus arctos*) to seasonality, a proxy in this case for habitat quality,
showing high home range overlap in areas of low and high seasonality and low
home range overlap in areas of moderate seasonality. Despite these, *missing
multilayer approach*.

>>>>

The emergent relationship between habitat and sociality has been explored by the
distribution and phenology of resources and use of social information. Cougars
had increased home range overlap in regions with high hunting opportunity, a
proxy for resource richness [@Elbroch_2016]. Caribou showed seasonal differences
in sociality, where social associations were high in winter and contrastingly
low in summer when resource availability is homogenous [@Peigner_2019]. Bison
(*Bison bison*) showed stronger habitat selection when group size was larger and
avoidance of predation risk was a main factor contributing to their habitat
selection [@Fortin_2009]. <!--Despite these, *missing multilayer approach*.-->
